Exact method for the multi-product p-batch processing time maximization problem

### 2023-10-05 manuscript/manuscript.tex
updating paper

\title{Multi-product Batch Processing Time Maximization Problem}

@@

It is importante to note that some production units are capable of processing multiple jobs at the same time. In such a case batches of different products and sizes can be grouped and processed by these units as a single batch. It is therefore necessary to determine the set of "batches" that each new grouped batch will contain. The multi-product balancing problem consists of determining these groupings, seeking to minimize the overall makespan. \cite{KashanOzturk2022} name this problem \emph{p-batch} (parallel batching) in contradiction with the \emph{s-batch} (serial batching) problem where jobs are processed one by one over production facilities, as described before.  However, in the best of our knowledge, few works consider p-patch multi-product batch problems. One exception is the work of \cite{LiEtAl2022} which deal with a multi-product \emph{p-batch} \emph{s-batch} problem involving incompatible families with different job sizes and capacity constraints.

@@

In this work we are interested in the multiperiod multi-product batch scheduling problem in a networked plant that arises in a plastic bag industry. The industrial plant of this company is very similar to the multi-product s-batch networked plant of the steel industry presented by \cite{LiuEtAl2020}, however, the production process in this plastic bags industry begins in extruders, which are production units capable of processing different batches simultaneously. Therefore the problem we are interested is a multi-product \emph{p-batch} \emph{s-batch} problem in a networked plant close to the problem addressed by \cite{LiEtAl2022}. Thus, part of the problem solving process consists of solving a multi-product p-batch problem into extruders. Also, in the problem we study, in addition to demand, we must consider the factory and outlets' storage capacity, which is individually defined for products, but also for the set of products.

@@

\section{Multi-product batch processing time maximization problem}
\label{sec:MBPTMP}

The multi-product batch processing time maximization problem arises when a set of different products are processed simultaneously in a same production batch. In this problem, it is considered that the quantity produced of each product is directly proportional to the processing time, however, with a different constant of proportionality (production rate) for each product. In addition, there is a maximum quantity allowed for the production of batch products, defined both individually and for the set. The production quantity of each product is mainly defined according to the demand for the product. However, it is still possible to stock the products and/or send them to the outlets. In both cases, there is a stocking/shipping limit for each product and a stocking/shipping limit for the set of products in the batch. Also, there is a time limit available for processing the batch. About the production, the industry manager has as priority to meet demand and he prefer to send the remaining production to outlets rather then stock it in the factory.

@@

O método proposto neste artigo para solução do MBPTM problem é composto por duas partes distintas, que são: a) cálculo do tempo máximo de processamento do lote multi-produtos; e b) cálculo e distribuição da produção entre a demanda, os outlets e o estoque em fábrica. A seguir, explicamos cada uma destas partes detalhadamente.

\noindent \emph{cálculo do tempo máximo de processamento do lote multi-produtos:}

@@

\noindent where $T'$ é o tempo máximo de processamento cuja produção será utilizada exclusivamente para atendimento da demanda.

Neste caso, sendo $D_{i}^{'}$ a quantidade produzida do produto $i$ após $T'$ unidades de tempo de processamento do lote, temos que:

@@

\noindent e, como $D_{i}^{'} \leq D_i$, $\forall i$, temos que:

@@

Das equações em (\ref{eq:s02}), (\ref{eq:s03}) e (\ref{eq:s04}), temos:

@@

E, como desejamos máximo valor para $T'$, de (\ref{eq:s05}), temos:

@@

Observer que poderá haver uma sobra correspondente à demanda não atendida pela produção ocorrida na primeira parte do tempo de processamento do lote, $T'$. Esta sobra, $S_i$, será definida de acordo com as equações em (\ref{eq:s07}):

@@

É possível também considerar que os outlets são uma extensão do estoque da fábrica. Portanto it is possible to consider the factory stock of product $i$ and the outlets stock $i$ as single stock for the product $i$, de forma que:

@@

\noindent where $E_i$ is the sum of factory stock and outlets stock of the product $i$.

Como o tempo $T'$ foi utilizado apenas para produção que irá atender à demanda, $T''$ será o restante do tempo de processamento, ou seja, o tempo máximo de processamento utilizado para produção que irá atender à sobra da demanda, será enviada para os outlets e estocada em fábrica. Assim temos que:

@@

Portanto, das restrições em (\ref{eq:s09}) e equações em (\ref{eq:s12}), temos:

@@

\noindent e, das restrições em (\ref{eq:s10}) e equações em (\ref{eq:s12}), temos:

@@

Finalmente, como $T''$ é um valor inteiro e queremos maximizar esse valor, então:

@@

Note that, à medida em que reduzimos o valor de $T'$, a consequente redução do valor de $D_{i}^{'}$ será atribuída diretamente à sobra $S_i$ e, portanto, there will be no change in the optimal solution if it is considered to $T'$, a value between 0 and the value found in step 1. Thus it is possible to use a simplification of the method presented, making $T' = 0$. In this case $S_i = \textrm{UD}_i, \forall i$. The simplified version of the method is presented below:

@@

Essa simplificação do método demonstra que o valor ótimo calculado para $T$ não depende da forma como a produção do produto $i$, $P_i$, é distribuída entre atendimento à demanda, $D_i$, outlets, $O_i$, e estoque de fábrica $I_i$.

We can determine now the values of $D_i$, $O_i$ and $I_i$, $\forall i$, simply by seguindo the priorities for distribution. The following three algorithms can be used to find a complete solution.

The algorithm (\ref{alg:part01}) is used for finding an optimimal value fot $T$.

@@

Then an initial production distribution can be done by the algorithm (\ref{alg:part02}). Esta distribuição é feita sem levar em consideração as restrições definidas para o conjunto de produtos do lote. $SO$ e $SI$ representam, respectivamente, o quantidade total disponível a ser enviada para os outlets e a quantidade total disponível para estoque em fábrica após a distribuição inicial. Caso esse valores sejam negativo, isso indica que a distribuição inicial proposta não é uma distribuição viável.

@@

Assim, after applying algorithm (\ref{alg:part02}), if $SO \geq 0$ and $SI \geq 0$, solution found is an optimal solution. However, if $SO < 0$ or $SI <0$, solution is not yet feasible. But as the solution found to $T$ is feasible to the problem defined in (\ref{MBPTMP01}) to (\ref{MBPTMP10}), we have the following statements:

@@

Therefore it is possible to meet the restrictions by applying the agorithm (\ref{alg:part03}). Neste algoritmo redistribuimos a produção do estoque para os outlets ou vice versa, respectivamente, em função de termos um $SI$ ou $SO$ negativo.

\begin{algorithm}
\caption{Solving MBPTM problem | Part 03: redistribute production to comply with limitation restrictions for the batch products set.}\label{alg:part03}
\begin{algorithmic}
\Require $O_i, I_i, \textrm{UO}_i, \textrm{UI}_i, \forall i, SO, SI$.
\If{$SO < 0$}
\For{all $i$}
	\State $O_i \gets O_i - \min\{ O_i, UI_i, |SO|\}$
	\State $I_i \gets I_i + \min\{ O_i, UI_i, |SO|\}$
	\State $SO \gets SO + \min\{ O_i, UI_i, |SO|\}$
	\If{$SO = 0$}
		break looping for;
	\EndIf
\EndFor
\EndIf

@@

>>>>

\title{Exact method for the multi-product p-batch processing time maximization problem}

@@

It is importante to note that some production units are capable of processing multiple jobs at the same time. In such a case batches of different products and sizes can be grouped and processed by these units as a single batch. It is therefore necessary to determine the set of "batches" that each new grouped batch will contain. The multi-product balancing problem consists of determining these groupings, seeking to minimize the overall makespan. \cite{KashanOzturk2022} name this problem \emph{p-batch} (parallel batching) in contradiction with the \emph{s-batch} (serial batching) problem where jobs are processed one by one over production facilities, as described before.  \cite{FowlerMonch2022} present a taxonomy and an extensive literature review for the p-batch problems. Not mentioned by \cite{FowlerMonch2022}, \cite{LiEtAl2022} deal with a multi-product \emph{p-batch} \emph{s-batch} problem involving incompatible families with different job sizes and capacity constraints.

@@

In this work we are interested in the multiperiod multi-product batch scheduling problem in a networked plant that arises in a plastic bag industry. The industrial plant of this company is very similar to the multi-product s-batch networked plant of the steel industry presented by \cite{LiuEtAl2020} (Fig. \ref{fig:networkdPlantSteelIndustry}), however, the production process in this plastic bags industry begins in extruders, which are production units capable of processing different batches simultaneously. Therefore the problem we are interested is a multi-product \emph{p-batch} \emph{s-batch} problem in a networked plant close to the problem addressed by \cite{LiEtAl2022}. Thus, part of the problem solving process consists of solving a multi-product p-batch problem into extruders. Also, in the problem we study, in addition to demand, we must consider the factory and outlets' storage capacity, which is individually defined for products, but also for the set of products.

@@

\section{Multi-product p-batch processing time maximization problem}
\label{sec:MBPTMP}

The multi-product p-batch processing time maximization problem arises when a set of different products are processed simultaneously in a same production batch. In this problem, it is considered that the quantity produced of each product is directly proportional to the processing time, however, with a different constant of proportionality (production rate) for each product. In addition, there is a maximum quantity allowed for the production of batch products, defined both individually and for the set. The production quantity of each product is mainly defined according to the demand for the product. However, it is still possible to stock the products and/or send them to the outlets. In both cases, there is a stocking/shipping limit for each product and a stocking/shipping limit for the set of products in the batch. Also, there is a time limit available for processing the batch. About the production, the industry manager has as priority to meet demand and he prefer to send the remaining production to outlets rather then stock it in the factory.

@@

The method proposed in this paper for solution of the MPBPTM problem is composed of two distinct parts, which are: a) calculation of the maximum processing time of the predefined multi-product p-batch; and b) calculation of the production to meet demand, the production sent to outlets and the production stocked in factory. Next, we explain each of these parts in detail. \\

\noindent \emph{Calculation of maximum p-batch processing time:} \\

@@

\noindent where $T'$ is the maximum processing time whose production will be used exclusively to meet the demand.

Then, being $D_{i}^{'}$ the quantity produced of the product $i$ after $T'$ units of processing time, we have:

@@

\noindent and, as $D_{i}^{'} \leq D_i$, $\forall i$, we have:

@@

From the equations in (\ref{eq:s02}) and the restrictions in (\ref{eq:s03}) and (\ref{eq:s04}), we have:

@@

And, as we wish maximum value to $T'$, from (\ref{eq:s05}) we have:

@@

Observe that there may be a leftover corresponding to the demand not met by the production in the first part of the processing time, $T'$. This leftover, $S_i$, will be defined according to the equations in (\ref{eq:s07}):

@@

It is also possible to consider that outlets are extensions of the factory stock. Therefore, it is possible to consider the factory stock of product $i$ and the outlets stock $i$ as single stock for the product $i$, $E_i$, so that:

@@

As the time $T'$ was used only for production that will meet the demand, $T''$  will be the remaining processing time, \emph{i.e.} the maximum processing time used for production that will meet the leftover of demand, sent to the outlets and stored in factory. So we have:

@@

\noindent Thus, after replacing (\ref{eq:s12}) in (\ref{eq:s09}) and applying some algebra, we have:

@@

\noindent And, after replacing (\ref{eq:s12}) in (\ref{eq:s10}) and applying some algebra, we have:

@@

Finally, as $T$  is an integer value and we want to maximize this value, then:

@@

Note that, as we reduce the value of $T'$, the consequent reduction of $D_{i}^{'}$ will be directly attributed to the leftover of demand $S_i$ and, therefore, there will be no change in the optimal solution if it is considered to $T'$, a value between 0 and the value found in step 1. Thus it is possible to use a simplification of the method presented, making $T' = 0$. In this case $S_i = \textrm{UD}_i, \forall i$. The simplified version of the method is presented below:

@@

This simplification of the method demonstrates that the great value calculated to $T$ does not depend on the way the production of the product $i$, $P_i$, is distributed between service to demand, $D_i$, outlets, $O_i$, and  factory's stock $I_i$.

We can determine now the values of $D_i$, $O_i$ and $I_i$, $\forall i$, simply attending the priorities for distribution. The following three algorithms can be used to find a complete solution.

The Algorithm (\ref{alg:part01}) is used for finding an optimimal value for $T$.

@@

Then an initial production distribution can be done by the Algorithm (\ref{alg:part02}). This distribution is made without considering the restrictions defined for the set of products. $SO$ and $SI$ represent, respectively, the total amount available to be sent to the outlets and the total amount available for factory inventory after the initial distribution. If this values are negative, this indicates that the proposed initial distribution is not a feasible distribution.

@@

Assim, after applying Algorithm (\ref{alg:part02}), if $SO \geq 0$ and $SI \geq 0$, solution found is an optimal solution. However, if $SO < 0$ or $SI <0$, solution is not yet feasible. But as the solution found to $T$ is feasible to the problem defined in (\ref{MBPTMP01}) to (\ref{MBPTMP10}), we have the following statements:

@@

Therefore it is possible to meet the restrictions by applying the Agorithm (\ref{alg:part03}). In this algorithm we redistributed the production of factory's stock to the outlets or vice versa, respectively, due to having a $SI$ or $SO$ negative.

\begin{algorithm}
\caption{Solving MBPTM problem | Part 03: redistribute production to comply with limitation restrictions for the batch set.}\label{alg:part03}
\begin{algorithmic}
\Require $O_i, I_i, \textrm{UO}_i, \textrm{UI}_i, \forall i, SO, SI$.
\If{$SO < 0$}
\For{all $i$}
	\State $O_i \gets O_i - \min\{ O_i, UI_i, |SO|\}$
	\State $I_i \gets I_i + \min\{ O_i, UI_i, |SO|\}$
	\State $SO \gets SO + \min\{ O_i, UI_i, |SO|\}$
	\If{$SO = 0$}
		break looping for;
	\EndIf
\EndFor
\EndIf

@@

\bibitem[\protect\citeauthoryear{Fowler and Mönch}{2022}]{FowlerMonch2022}
Fowler, J.W. and Mönch, L. (2022). A survey of scheduling with parallel batch (p-batch) processing. {\it European Journal of Operational Research}, Vol. 298, pp. 1--24.

\bibitem[\protect\citeauthoryear{Fowler and Mönch}{2022}]{FowlerMonch2022}
Fraga, T.B. (2023). COPSolver: open source software for solving combinatorial optimization and other decision prob-
lems - library for solving the multi-product p-batch processing time maximization problem {\it Software Impacts}, invited paper, in press.
